\Huge Conferences in an Era of Expensive Carbon

### 2019-06-11 main.tex
Fiddling

\SECTION{Putting a Price on Emissions}

@@

To be effective in the long term, a carbon price needs to be uniform across
society---i.e., it should be imposed by governments.  Indeed, many
countries\bcp{e.g.?} and states (e.g., California) have already adopted
carbon pricing policies; more will follow.
%
Bottom line: We are entering an era in which carbon will be expensive.

Anticipating this era, what should we rationally do now to ensure that ACM,
and computer-science research more broadly, continue to thrive in a world
where air travel is more expensive?  Believing that it needs to come quickly
to avert disaster, what can we do to accelerate the process? \mwh{The
  question now seems to have changed. The paper started by saying ACM has an
  ``especially important role to play,'' but now seems to suggest it should
  be reacting to an inevitable/coming future. These questions probably need
  to go much earlier, and the earlier text reworked around them.}
\bcp{I tried rewording the opening of the second paragraph to address this.}

\SECTION{Carbon Offsets}

@@

Carbon offsets do come with some significant concerns.
%
One superficial impediment is that most organizations do not currently have
accounting procedures in place to deal with them, and the piecemeal
political and bureaucratic work of designing and implementing a separate
policy for each organization can consume significant energy.
%
Another point to be careful of is that the long-term climate benefit of some
offsetting strategies (for example, paying people to plant trees) is
controversial.
%
A more fundamental problem is that it is hard to decide how
much one should pay to offset a ton of carbon: current prices vary
significantly 
around an average of around \$15 per ton, depending on the vendor, the
nature of the offset project, the region of the world where it will be
implemented, etc.  Moreover, in order for offsets (or any other form of a
carbon pricing) to fully motivate the needed changes in behavior, the price
may need to go much higher---the true ``social cost'' of a ton of carbon is
variously estimated at anywhere from \$40 to \$400 per
ton~\bcp{citation}---and setting it too low may encourage complacency.
%
However, while acknowledging these concerns, we believe that voluntary
carbon offsetting can be an effective near-term tool for raising awareness
and beginning to shift organizational behavior because it associates
emissions with a number, giving decision makers within the organization
something concrete to optimize.

\SECTION{Measure, Analyze, Optimize}

@@

Discussions about the future of conferences also require data.  
%
% Beyond imposing a price on our carbon footprint (or waiting for one
% to be imposed from outside), a sane response to climate change should
% clearly also include taking steps to reduce the size of this
% footprint.
% \mwh{Don't like previous sentence. It seems to have gotten away from
%   the point of the paper, which is using price to change balance of
%   apples to oranges. Analyzing data is useful for figuring out ACM's
%   internal price, not tweaking around the edges, which is how it reads
%   below.} 
\bcp{Bad transition here.  The rest of this section needs reorg.}
For conferences, there are many options that one might
contemplate~\cite{ClimateCommitteReport}, from easy-but-incremental changes
like making program committee meetings virtual instead of physical and
enabling virtual participation via live-streaming, all the way to complete
re-imagining of conferences and their role in science (holding conferences
completely in virtual spaces, replacing conferences with journals, etc.),
with some intriguing hybrid forms in the middle (regional conferences,
mega-conferences, conferences held simultaneously at two locations on
different continents, etc.).
%
But before undertaking significant changes, we need to understand the
situation better.  For most of these ideas, it is hard to confidently
predict either the potential benefits (in terms of reduced emissions) or the
potential costs (to scientific exchange, career development of young
scientists, etc.).  Indeed, a preliminary analysis of registration data from
a number of SIGPLAN conferences paints a rather complicated picture.
%
\bcp{Put the discussion of Figure 1 (and an accompanying figure
showing distance traveled to several instances of the same conference) here;
this illustrates the difficulty and the need for careful data gathering and
analysis.} 
All parts of ACM should be doing this kind of analysis.  (The acm-climate
mailing list is one place to exchange ideas about this.)

\SECTION{Deeper Changes}

Ultimately, responding to the inevitability of expensive carbon may involve
rethinking the whole basis of how academic computer science is done.
\bcp{
\begin{itemize}
\item Add a bit of meat about how the current economic model may be
  unsustainable and reworking it will involve substantial organizational
  changes.  (There may be some good words that we can paraphrase from our
  second reviewer!)
\item monitoring and mitigating carbon costs should be an ACM-level activity
\end{itemize}
}

>>>>

\SECTION{Putting a Price on Carbon}

@@

To be effective in the long term, a carbon price needs to be uniform across
society---i.e., it should be imposed by governments.  Indeed, some 40
countries and more than 20 cities and states have already adopted
carbon pricing policies~\cite{pricingcarbon}; more will follow.
%
Bottom line: We are entering an era in which carbon will be expensive.

Anticipating this era, what should we rationally do now to ensure that 
computer-science research continues to thrive in a world
where air travel is more expensive?  Believing that it needs to come quickly
to avert disaster, what can we do to accelerate the process? \mwh{The
  question now seems to have changed. The paper started by saying ACM has an
  ``especially important role to play,'' but now seems to suggest it should
  be reacting to an inevitable/coming future. These questions probably need
  to go much earlier, and the earlier text reworked around them.}
\bcp{I tried rewording the opening of the second paragraph to address this.}

\SECTION{Starting Now}

@@

Carbon offsets also raise some significant concerns.
% %
% A superficial one is that most organizations do not currently have
% accounting procedures in place to deal with them, and the piecemeal
% political and bureaucratic work of designing and implementing a separate
% policy for each organization can consume significant energy.
%
One is that the long-term climate benefit of some offsetting strategies (for
example, paying people to plant trees) is controversial: it is important to
choose reputable vendors and projects (such as methane capture) whose
net benefit is clear.
%
A more fundamental problem is that it is hard to decide how
much one should pay to offset a ton of carbon: current prices vary
around an average of around \$15 per ton, depending on the vendor, the
nature of the offset project, the region of the world where it will be
implemented, etc.  Moreover, in order for offsets (or any other form of a
carbon pricing) to fully motivate the needed changes in behavior, the price
may need to go much higher---the true ``social cost'' of a ton of carbon is
variously estimated at anywhere from \$40 to \$400 per
ton~\bcp{citation}---and setting it too low may encourage complacency.
%
While acknowledging these concerns, we believe that voluntary
carbon offsetting can be an effective near-term tool for raising awareness
and beginning to shift organizational behavior because it associates
emissions with a number, giving decision makers within the organization
something concrete to optimize.

\SECTION{Grounding the Discussion}

@@

What, concretely, would it mean to ``optimize'' the carbon footprint of
conferences?
%
% Beyond imposing a price on our carbon footprint (or waiting for one
% to be imposed from outside), a sane response to climate change should
% clearly also include taking steps to reduce the size of this
% footprint.
% \mwh{Don't like previous sentence. It seems to have gotten away from
%   the point of the paper, which is using price to change balance of
%   apples to oranges. Analyzing data is useful for figuring out ACM's
%   internal price, not tweaking around the edges, which is how it reads
%   below.} 
One might contemplate a wide array of options~\cite{ClimateCommitteReport},
from easy-but-incremental changes like making program committee meetings
virtual instead of physical and enabling virtual participation via
live-streaming, all the way to complete re-imagining of conferences and
their role in science (holding conferences completely in virtual spaces,
replacing conferences with journals, etc.), with some intriguing hybrid
forms in the middle (regional conferences, mega-conferences, conferences
held simultaneously at two locations on different continents, etc.).
%
How much of a difference would these make to emissions?

% But before undertaking significant changes, we need to understand the
% situation better.  For most of these ideas, it is hard to confidently
% predict either the potential benefits (in terms of reduced emissions) or the
% potential costs (to scientific exchange, career development of young
% scientists, etc.).  
A preliminary analysis of registration data from
a number of SIGPLAN conferences paints a rather complicated picture.
%
\bcp{Put the discussion of Figure 1 (and an accompanying figure
showing distance traveled to several instances of the same conference) here;
this illustrates the difficulty and the need for careful data gathering and
analysis.}

All parts of ACM should be doing this kind of analysis.  (The acm-climate
mailing list is one place to exchange ideas about this.)

\SECTION{Plan Ahead}

Looking further ahead, the expectation of expensive carbon invites a deeper
rethinking of how academic computer science is done.  
%
\bcp{
\begin{itemize}
\item Add a bit of meat about how the current economic model may be
  unsustainable and reworking it will involve substantial organizational
  changes.  (There may be some good words that we can paraphrase from our
  second reviewer!)
\item monitoring and mitigating carbon costs should be an ACM-level activity
\end{itemize}
}
